### 2024-08-15 paper/main.tex
my version of adding in the new paragraph after PNAS review

\noindent The stimulus, represented as a cursor on the screen, would quickly move to one of the two target circles. Participants were instructed to reach the same target as the stimulus within a time constraint of 1500 ms. The time remaining in each trial was represented visually with a timing bar that decreased in width according to the elapsed time. Thus, participants were fully aware of how much time they had left relative to the time constraint. A trial was considered a win and the participant received one point if they successfully reached the same target as the stimulus within the time constraint (\boldblue{Fig. 1B}). A trial was considered incorrect and the participant received zero points if they reached the opposite target as the stimulus within the time constraint. A trial was considered an indecision and the participant received zero points if they failed to reach a target within the time constraint.

@@

Indecisions are often not studied since many decision-making tasks do not permit a non-response or simply do not consider responses made after some time constraint. A limitation of the commonly used two-alternative forced choice task without a time constraint is that the participant or animal must select one of two potential options, which does not allow for indecisive behaviour. For decision-making tasks with a time constraint, late responses beyond the deadline are typically not included in the analysis\autocite*{forstmannStriatumPreSMAFacilitate2008,diederichFurtherTestSequentialsampling2008,wuCapacityCognitiveControl2016,dambacherTimePressureAffects2015}. Furthermore, previous modeling work on decision-making under time constraints has primarily focused on the response times and response time distributions of correct and incorrect decisions \autocite*{karsilarSpeedAccuracyTradeoff2014,farashahiDynamicCombinationSensory2018}. However, a focus on only correct and incorrect decisions leaves out a crucial and prevalent aspect of decision-making—indecisive behaviour.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Methods %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2mm}
\SectionHeader{Methods}

@@

\noindent 44 participants participated across two experiments 20 individuals participated in \boldblue{Experiment 1} and 24 individuals participated in \boldblue{Experiment 2}. All participants reported they were free from musculoskeletal injuries, neurological conditions, or sensory impairments. In addition to a base compensation of \$5.00, we informed them they would receive a performance-based compensation of up to \$5.00. Participants received the full \$10.00 once they completed the experiment irrespective of their performance. All participants provided written informed consent to participate in the experiment and the procedures were approved by the University of Delaware’s Institutional Review Board.

>>>>

\noindent The stimulus, represented as a cursor on the screen, would quickly move to one of the two target circles. Participants were instructed to reach the same target as the stimulus within a time constraint of 1500 ms. The time remaining in each trial was represented visually with a timing bar that decreased in width according to the elapsed time. Thus, participants were fully aware of how much time they had left relative to the time constraint. A trial was considered a win and the participant received one point if they successfully reached the same target as the stimulus within the time constraint (\boldblue{Fig. 1B}). A trial was considered incorrect and the participant received zero points if they reached the opposite target as the stimulus within the time constraint. A trial was considered an indecision and the participant received zero points if they failed to reach a target within the time constraint. That is, we considered an indecision to be not reaching a target within the time constraint and thus failing to make a decision in time.

@@

Indecisions are often not studied since many decision-making tasks do not permit a non-response or simply do not consider responses made after some time constraint. A limitation of the commonly used two-alternative forced choice task without a time constraint is that the participant or animal must select one of two potential options, which does not allow for indecisive behaviour. For decision-making tasks with a time constraint, late responses beyond the deadline are typically not included in the analysis\autocite*{forstmannStriatumPreSMAFacilitate2008,diederichFurtherTestSequentialsampling2008,wuCapacityCognitiveControl2016,dambacherTimePressureAffects2015}. These studies tend to focus on  response times and response time distributions of correct and incorrect decisions. However, a focus on only correct and incorrect decisions leaves out a crucial and prevalent aspect of decision-making—indecisive behaviour.

Two different frameworks to model human decision-making are decision theoretic models (Berger 1985) and  drift-diffusion models (Ratcliff 2016 review)\autocite*{ratcliffDiffusionDecisionModel2008}. Decision theoretic models use knowledge of sensorimotor delays and uncertanties to select decisions that maximize reward (more citations)\autocite*{hudsonOptimalCompensationTemporal2008, otaMotorPlanningTemporal2015}. Drift-diffusion models characterize the decision-making process through a noisy decision variable that reaches some threshold to make a decision. However, unlike decision theoretic models, drift-diffusion models do not explicitly represent sensorimotor delays and uncertainties (e.g. reaction time, movement time, timing uncertainty, switch time), which is a critical factor when selecting optimal decisions.

Drift-diffusion models can capture indecisions through the decision variable failing to cross a threshold within a time constraint. Yet, prior work using these models for decision-making tasks under time constraints do not model indecisions\autocite*{karsilarSpeedAccuracyTradeoff2014, farashahiDynamicCombinationSensory2018}. Further, drift-diffusion models would indicate a guess decision through a noisy decision variable crossing a threshold at random. However, these models do not consider guessing as a separate process from reacting to a stimulus (i.e. a person consciously deciding when to guess). This notion of guessing being a separate process has been proposed by Yellot and colleaugues (1970, ADD TO BIB) in their fast-guess model. However, like drift-diffusion models, their modeling framweork also did not consider a representation of sensorimotor delays and uncertainties for optimal decision-making, which decision theoretic models have shown to be important for explaining human behaviour. In \boldblue{Experiment 1}, participants were required to account for sensorimotor delays and uncertainties to decide when to switch from waiting to react to making a guess. Thus, our modeling approach can be considered as a complementary blend between the decision-theoretic and fast-guess models.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%% Methods %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{2mm}
\SectionHeader{Methods}

@@

\noindent 44 participants participated across two experiments. 20 individuals participated in \boldblue{Experiment 1} and 24 individuals participated in \boldblue{Experiment 2}. All participants reported they were free from musculoskeletal injuries, neurological conditions, or sensory impairments. In addition to a base compensation of \$5.00, we informed them they would receive a performance-based compensation of up to \$5.00. Participants received the full \$10.00 once they completed the experiment irrespective of their performance. All participants provided written informed consent to participate in the experiment and the procedures were approved by the University of Delaware’s Institutional Review Board.
